\Large\textbf{Preparation GUIDE for Initial-Submission Manuscript}\\~\\ \large\textbf{ Preparation of Papers in Two-Column Format\\ for the ASP-DAC 2014 (\LaTeX2e version)}

### 2013-12-02 exps.tex
Updated exps

\section{Experimental results}
\label{sec:experimental-results}
% <<<<<<< HEAD
% \begin{table}[t]
%   \centering
%   \twocolumn[

%   \begin{@twocolumnfalse}
%     \caption{Benchmark programs using \texttt{delay} constructs} \label{table:benchmark}
%     \scalebox{0.85}{
%       \begin{tabular}{|c| c | c | c | c | c | c | c |}
% 	\cline{4-8}
% 	\multicolumn{3}{c|}{}											& HRTCS 		& Motor 		  & Robot 			  & AECS/CD1  		   & AECS/CD2\\ \hline
% 	\multirow{12}{*}{JOP} 		& \multicolumn{2}{|c|}{BCRT} 		&0.0334 ms 		& 0.0361 ms		  & 0.0325 ms		  & 0.1683 ms		   & 0.1881 ms\\ \cline{2-8}   
%         & \multicolumn{2}{|c|}{WCRT} 		&0.1120 ms 		& 0.1116 ms		  & 0.0601 ms		  & 0.7147 ms		   & 1.0115 ms\\ \cline{2-8} 
%         & \multirow{2}{*}{Delay 1}	 & M..N &50.3-200.3 ms 	& 2.4-7.4772 ms	  & 1230-2274.0263 ms & 10000-42473.2197 ms& 10000-53772.0045 ms \\ \cline{3-8} 
%         &			   & d			 		&1506-1787  	& 67 			  & 37861			  & 59427		       &53160\\ \cline{2-8}
%         & \multirow{2}{*}{Delay 2}	 & M..N & 	N/A 		& 1.667-5.2452 ms & N/A				  & N/A 			   &10000-53772.0045 ms\\ \cline{3-8} 
%         &			   & d			 		& 	N/A	 		& 47			  & N/A				  & N/A       		   &53160\\ \cline{2-8}
%         & \multirow{2}{*}{Delay 3}	 & M..N & 	N/A	 		& 0.05-0.2232 ms  & N/A				  & N/A       		   &N/A\\ \cline{3-8} 
%         &			   & d			 		& 	N/A	 		& 2		      	  &	N/A				  & N/A       		   &N/A\\ \cline{2-8}
%         & \multirow{2}{*}{Delay 4}	 & M..N & 	N/A	 		& 0.3-1.0044 ms   & N/A				  &	N/A       		   &N/A\\ \cline{3-8} 
%         &			   & d				 	& 	N/A	 		& 9				  & N/A				  &	N/A      		   &N/A\\ \cline{2-8}
%         & \multirow{2}{*}{Delay 5}	 & M..N & 	N/A	 		& 0.733-2.3436 ms & N/A				  &	N/A      		   &N/A\\ \cline{3-8} 
%         &			   & d			 		& 	N/A	 		& 21 			  &	N/A				  & N/A      		   &N/A\\ \hline
% 	\multirow{12}{*}{TP-JOP} 	& \multicolumn{2}{|c|}{BCRT} 		&0.0028 ms 		& 0.0060 ms		  & 0.0011 ms		  & 0.0532 ms		   & 0.0292 ms\\ \cline{2-8}   
%         & \multicolumn{2}{|c|}{WCRT} 		&0.0329 ms 		& 0.0393 ms		  & 0.0361 ms		  & 0.5072 ms		   & 0.8388 ms\\ \cline{2-8} 
%         & \multirow{2}{*}{Delay 1}	 & M..N &50.3-600.3 ms 	& 2.4-15.6265 ms  & 1230-42317.8276 ms& 10000-95358.8578 ms& 10000-287757.9834 ms \\ \cline{3-8} 
%         &			   & d			 		&18209-18232 	& 398 			  & 1171429			  & 188015		       &343054\\ \cline{2-8}
%         & \multirow{2}{*}{Delay 2}	 & M..N & 	N/A 		& 1.667-10.8757 ms& N/A				  & N/A 			   &10000-287757.9834 ms\\ \cline{3-8} 
%         &			   & d			 		& 	N/A	 		& 277			  & N/A				  & N/A       		   &343054\\ \cline{2-8}
%         & \multirow{2}{*}{Delay 3}	 & M..N & 	N/A	 		& 0.05-0.3534 ms  & N/A				  & N/A       		   &N/A\\ \cline{3-8} 
%         &			   & d			 		& 	N/A	 		& 9		      	  &	N/A				  & N/A       		   &N/A\\ \cline{2-8}
%         & \multirow{2}{*}{Delay 4}	 & M..N & 	N/A	 		& 0.3-1.9631 ms   & N/A				  &	N/A       		   &N/A\\ \cline{3-8} 
%         &			   & d				 	& 	N/A	 		& 50			  & N/A				  &	N/A      		   &N/A\\ \cline{2-8}
%         & \multirow{2}{*}{Delay 5}	 & M..N & 	N/A	 		& 0.733-4.79 ms   & N/A				  &	N/A      		   &N/A\\ \cline{3-8} 
%         &			   & d			 		& 	N/A	 		& 122 			  &	N/A				  & N/A      		   &N/A\\ \cline{2-8}
% 	\hline
%       \end{tabular}
%     }
%   \end{@twocolumnfalse}
%   ]

@@

We have carried out a number of experiments on a set of applications
with real-time constraints. The characteristics of the benchmark set
including required real-time delays and program sizes are shown in
Table~\ref{fig:benchlist}.

@@

As a first step, BCRT and WCRT were calculated for all examples. Given
the real-time \mbox{\texttt{delay (M..N)}} provided by programmers,
required logical delay \textit{d} was determined by applying
Algorithm~\ref{alg:1}. In HRTCS, real-time delay of the range
50.3..200.3 (ms) is only satisfied when \emph{d} is between 1506 and
1787 (as shown previously in
Section~\ref{sec:find-logic-delay}). Similarly, Printer/CD2 satisfies
real-time ranges of 1.2..30.3 (ms) and 5.6..100.2 (ms) when \emph{d} is
46..617 and 213..2041, respectively. It is then the compiler's job to
statically choose one of the values in this range.

% The upper bound \texttt{N} needed to be relaxed for all examples other
% than HRTCS to obtain a feasible \texttt{d}. Therefore,
On the other hand, Algorithm \ref{alg:2} is applied to those examples,
where relaxation was required, to determine the minimum upper real-time
bound \emph{N} such that there exists a solution for \emph{D} in
Algorithm \ref{alg:1}. This algorithm gives a unique number for logical
tick delay \emph{d} such that \emph{d} = Min(\emph{$S_2$}) =
Max(\emph{$S_1$}). The compiler, therefore, will choose \emph{d} based
on the newly computed \emph{N} for the examples: Printer/CD1, Motor and
AECS.

@@

The previous results show that HRTCS and Printer/CD2 were the only
examples that the compiler was able to find \textit{d} without relaxing
upper bound of \texttt{delay}. Figure~\ref{fig:graph} shows the accuracy
of our results by comparing differences between programmer specified
upper bounds (Table~\ref{fig:benchlist}) and the actual bounds obtained
using our techniques (Table~\ref{fig:comparison}).

\begin{figure}[h!]
	\centering
\begin{tikzpicture}[scale=0.9]
	\begin{axis}[
			ybar,xtick=data,
			symbolic x
			coords={HRTCS,Printer/CD1,Printer/CD2,AECS/CD1,AECS/CD2},
			height=5cm,
			width=9.5cm,
			minor y tick num=1,
			ymajorgrids=true,
			ytick={0,...,5},
%      xlabel=Benchmark,
			x tick label style={rotate=45,font=\footnotesize},
			ylabel=Difference factor,
		]
			\addplot coordinates
			{(HRTCS,1)(Printer/CD1,1.6)(Printer/CD2,1)(AECS/CD1,4.25)(AECS/CD2,5.39)};
			\addplot coordinates {(Printer/CD2, 1)(AECS/CD2, 5.39)};
	\end{axis}
\end{tikzpicture}
\begin{tikzpicture}[scale=0.9]
	\begin{axis}[
			ybar,xtick=data,
			symbolic x coords={Motor},
			ytick={0,...,5},
			ymin={1.5},
			minor y tick num=1,
			ymajorgrids=true,
%      extra y ticks={2.5},
%      extra y tick labels={asdf},
%      extra y tick style={grid=major},
			height=5cm,
			width=9.5cm,
			xlabel=Benchmark,
			xlabel shift={4pt},
			ylabel=Difference factor,
			legend style={
				anchor=north,
				at={(0.45,-0.44)},
				legend columns=-1,
			}
%      nodes near coords
		]
			\addplot coordinates {(Motor, 3.54)};
			\addplot coordinates {(Motor, 3.15)};
			\addplot coordinates {(Motor, 4.46)};
			\addplot coordinates {(Motor, 3.35)};
			\addplot coordinates {(Motor, 2.81)};
			\legend{Delay1,Delay2,Delay3,Delay4,Delay5}
	\end{axis}
\end{tikzpicture}
\caption{Accuracy of the results}
\label{fig:graph}
\end{figure}

There are two influential factors in determining the relaxation: 1)
execution speed of a target platform and 2) the nature of the program
that runs on this platform. Clock frequency of the processor directly
impacts the value of WCRT. On the other hand, programmer can write a
program such that large data computations in a single logical tick
increase WCRT of the program. Assuming we do not change the architecture
of the execution platform (i.e. JOP), the difference factor can only be
reduced by modifying the benchmark programs such that the critical paths
are broken up using \texttt{pause} constructs, thereby reducing the
WCRT.

@@

% As one can see in Figure \ref{fig:comparison}, BCRT and WCRT of overall programs
% are smaller when they run on TP-JOP. For example, WCRT and BCRT of HRTCS are
% \(\times\)11.9 and \(\times\)3.4 smaller, respectively, for TP-JOP (0.0028,
% 0.0329 ms) compared to JOP (0.0334, 0.1120 ms). On the other hand, required
% logical delays \emph{d} are generally bigger on TP-JOP e.g. \(\times\)4.5 -
% \(\times\)5.9 and \(\times\)30.9 in Motor and Robot respectively. It is expected
% as their BCRT and WCRT differences are bigger on TP-JOP.
% This also led to greater increase in minimum upper real-time bounds \emph{N} for
% TP-JOP in every example.
% In AECS, there are two clock-domains using delay constructs that each has their
% own BCRT and WCRT. Again, individual BCRT and WCRT is smaller whereas \emph{d}
% is bigger on TP-JOP. One important property to note here, is that BCRT and WCRT
% of any clock-domains are invariant of \emph{d} as explained in Section
% \ref{sec:intr-real-time}. It is our fundamental assumption to find \emph{d} in
% our benchmark programs.
% >>>>>>> 4bffc4b1a43388f5ebf6cc737b9d3b246ee77dc7
{\renewcommand{\arraystretch}{0.9}
\begin{table}[t]
	\small
	\centering
	\caption{An overview of the benchmark programs}
	\label{fig:benchlist}
	\scalebox{0.9}{
		\begin{tabular}{llp{0.5cm}p{1cm}}
\toprule
\emph{Benchmark}       & \emph{Delay constructs used in each CD} & \emph{\# of CDs} & 
\emph{Lines of code}        
\\ \midrule
HRTCS                  & \texttt{delay(50.3..200.3 ms)} ($CD1$) & 2                  & 56
\\ \midrule
\multirow{5}{*}{Motor} & \texttt{delay(2.4..2.4 ms)}        & \multirow{5}{*}{1} & \multirow{5}{*}{116} \\ 
											 & \texttt{delay(1.667..1.667 ms)}      &                    &                      \\ 
											 & \texttt{delay(0.05..0.05 ms)}       &                    &                      \\ 
											 & \texttt{delay(0.3..0.3 ms)}        &                    &                      \\ 
											 & \texttt{delay(0.733..0.733 ms)}      &                    &
\\ \midrule
\multirow{3}{*}{Printer}
& \texttt{delay(2.7..10.6 ms)} ($CD1$)      & \multirow{3}{*}{2}        & \multirow{3}{*}{39} \\
& \texttt{delay(1.2..30.3 ms)} ($CD2$)		  &														&											\\
& \texttt{delay(5.6..100.2 ms)} ($CD2$)     &														&											
\\ \midrule
\multirow{2}{*}{AECS} & \texttt{delay(10000 ms)} ($CD1$) 
& \multirow{2}{*}{2} & \multirow{2}{*}{267} \\
& \texttt{delay(10000..10000 ms)} ($CD2$) & &
\\ \bottomrule
\end{tabular}
}
\vspace{-20pt}
\end{table}
}

{\renewcommand{\arraystretch}{0.6}
\begin{table}[t!]
\twocolumn[
\centering
\begin{@twocolumnfalse}
	\caption{Actual delays obtained for \texttt{delay} constructs in the
benchmark programs based on their BCRT and WCRT}
\begin{tabular}{ c c l l l l l l }
	\toprule
	\multicolumn{2}{c}{} & \emph{HRTCS} & \emph{Motor} & \emph{Printer/CD1} &
	\emph{Printer/CD2} & \emph{AECS/CD1} &	\emph{AECS/CD2} \\ 
	\midrule
	\multicolumn{2}{c}{\emph{BCRT}}	& 0.0334 ms	& 0.0361 ms & 0.009613 ms &
	0.0263 ms & 0.1683 ms & 0.1881 ms\\ 
	\cmidrule(r){1-8}
	\multicolumn{2}{c}{\emph{WCRT}} &0.1120 ms & 0.1116 ms & 0.0603 ms
	& 0.0491 ms & 0.8148 ms & 1.0115 ms\\ 
	\cmidrule(r){1-8}

	\multirow{2}{*}{Delay 1} & M..N & 50.3-200.3 ms	& 2.4-8.4882 ms	  &
	2.7-16.9378 ms & 1.2-30.3 ms & 10000-42483.2198 ms& 10000-53882.0045 ms \\
	\cmidrule(r){2-8}
	& d &1506-1888 & 68 & 281 & 46-617 & 59428 &53160\\ 
	\cmidrule(r){1-8}
	\multirow{2}{*}{Delay 2} & M..N & N/A & 1.668-5.2452 ms & N/A &
	5.6-100.2 ms & N/A &10000-53882.0045 ms\\ 
	\cmidrule(r){2-8}
	& d & N/A & 48 & N/A & 213-2041 & N/A &53160\\ 
	\cmidrule(r){1-8}
	\multirow{2}{*}{Delay 3} & M..N & N/A & 0.05-0.2232 ms & N/A & N/A & N/A
	&N/A\\ 
	\cmidrule(r){2-8}
	& d & N/A & 2 & N/A & N/A & N/A &N/A\\ 
	\cmidrule(r){1-8}
	\multirow{2}{*}{Delay 4} & M..N & N/A & 0.3-1.0044 ms & N/A & N/A & N/A
	&N/A\\ 
	\cmidrule(r){2-8}
	& d & N/A & 9 & N/A & N/A & N/A &N/A\\ 
	\cmidrule(r){1-8}
	\multirow{2}{*}{Delay 5} & M..N & N/A & 0.833-2.3436 ms & N/A & N/A & N/A
	&N/A\\ 
	\cmidrule(r){2-8}
	& d & N/A & 21 & N/A
	& N/A & N/A &N/A\\ \bottomrule
\end{tabular}
\label{fig:comparison}
\end{@twocolumnfalse}
]
\end{table}
}

>>>>

\section{Experimental results}
\label{sec:experimental-results}

@@

We have carried out a number of experiments on a set of applications
with real-time constraints. The characteristics of the benchmark set
including required real-time delays and program sizes are shown in
Table~\ref{fig:benchlist}.
{\renewcommand{\arraystretch}{0.9}
\begin{table}[h!]
	\small
	\centering
	\caption{An overview of the benchmark programs}
	\label{fig:benchlist}
	\scalebox{0.9}{
		\begin{tabular}{llp{0.5cm}p{1cm}}
\toprule
\emph{Benchmark}       & \emph{Delay constructs used in each CD} & \emph{\# of CDs} & 
\emph{Lines of code}        
\\ \midrule
HRTCS                  & \texttt{delay(50.3..200.3 ms)} ($CD1$) & 2                  & 56
\\ \midrule
\multirow{5}{*}{Motor} & \texttt{delay(2.4..2.4 ms)}        & \multirow{5}{*}{1} & \multirow{5}{*}{116} \\ 
											 & \texttt{delay(1.667..1.667 ms)}      &                    &                      \\ 
											 & \texttt{delay(0.05..0.05 ms)}       &                    &                      \\ 
											 & \texttt{delay(0.3..0.3 ms)}        &                    &                      \\ 
											 & \texttt{delay(0.733..0.733 ms)}      &                    &
\\ \midrule
\multirow{3}{*}{Printer}
& \texttt{delay(2.7..10.6 ms)} ($CD1$)      & \multirow{3}{*}{2}        & \multirow{3}{*}{39} \\
& \texttt{delay(1.2..30.3 ms)} ($CD2$)		  &														&											\\
& \texttt{delay(5.6..100.2 ms)} ($CD2$)     &														&											
\\ \midrule
\multirow{2}{*}{AECS} & \texttt{delay(10000 ms)} ($CD1$) 
& \multirow{2}{*}{2} & \multirow{2}{*}{267} \\
& \texttt{delay(10000..10000 ms)} ($CD2$) & &
\\ \bottomrule
\end{tabular}
}
\end{table}
}
{\renewcommand{\arraystretch}{0.6}
\begin{table*}[t!]
\centering
	\caption{Actual delays obtained for \texttt{delay} constructs in the
benchmark programs based on their BCRT and WCRT}
\begin{tabular}{ c c l l l l l l }
	\toprule
	\multicolumn{2}{c}{} & \emph{HRTCS} & \emph{Motor} & \emph{Printer/CD1} &
	\emph{Printer/CD2} & \emph{AECS/CD1} &	\emph{AECS/CD2} \\ 
	\midrule
	\multicolumn{2}{c}{\emph{BCRT}}	& 0.0.0396 ms	& 0.0425 ms & 0.0190 ms &
	0.0263 ms & 0.1784 ms & 0.1284 ms\\ 
	\cmidrule(r){1-8}
	\multicolumn{2}{c}{\emph{WCRT}} &0.1152 ms & 0.1096 ms & 0.0647 ms
	& 0.0491 ms & 0.3476 ms & 0.2991 ms\\ 
	\cmidrule(r){1-8}

	\multirow{2}{*}{Delay 1} & M..N & 50.3-200.3 ms	& 2.4-6.2493 ms	  &
	2.7-10.6 ms & 1.2-30.3 ms & 10000-19484.3481 ms& 10000-23278.2752 ms \\
	\cmidrule(r){2-8}
	& d &1272-1739 & 57 & 143-163 & 46-617 & 56062 &77844\\ 
	\cmidrule(r){1-8}
	\multirow{2}{*}{Delay 2} & M..N & N/A & 1.668-4.3855 ms & N/A &
	5.6-100.2 ms & N/A &10000-23278.2752 ms\\ 
	\cmidrule(r){2-8}
	& d & N/A & 40 & N/A & 213-2041 & N/A &53160\\ 
	\cmidrule(r){1-8}
	\multirow{2}{*}{Delay 3} & M..N & N/A & 0.05-0.2193 ms & N/A & N/A & N/A
	&N/A\\ 
	\cmidrule(r){2-8}
	& d & N/A & 2 & N/A & N/A & N/A &N/A\\ 
	\cmidrule(r){1-8}
	\multirow{2}{*}{Delay 4} & M..N & N/A & 0.3-0.8771 ms & N/A & N/A & N/A
	&N/A\\ 
	\cmidrule(r){2-8}
	& d & N/A & 8 & N/A & N/A & N/A &N/A\\ 
	\cmidrule(r){1-8}
	\multirow{2}{*}{Delay 5} & M..N & N/A & 0.733-1.9735 ms & N/A & N/A & N/A
	&N/A\\ 
	\cmidrule(r){2-8}
	& d & N/A & 18 & N/A
	& N/A & N/A &N/A\\ \bottomrule
\end{tabular}
\label{fig:comparison}
\end{table*}
}

@@

As a first step, BCRT and WCRT were calculated for all examples. Given
the real-time \mbox{\texttt{delay (M..N)}} provided by programmers,
required logical delay \textit{d} was determined by applying
Algorithm~\ref{alg:1}. In HRTCS, real-time delay of the range
50.3..200.3 (ms) is only satisfied when \emph{d} is between 1272 and
1739 (as shown previously in Section~\ref{sec:find-logic-delay}). Delay
2.7..10.6 (ms) is satisfied in Printer/CD1 with \emph{d} of 143..163.
Similarly, Printer/CD2 satisfies real-time ranges of 1.2..30.3 (ms) and
5.6..100.2 (ms) when \emph{d} is 46..617 and 213..2041, respectively. It
is then the compiler's job to statically choose one of the values in
this range.

% The upper bound \texttt{N} needed to be relaxed for all examples other
% than HRTCS to obtain a feasible \texttt{d}. Therefore,
On the other hand, Algorithm \ref{alg:2} is applied to those examples,
where relaxation was required, to determine the minimum upper real-time
bound \emph{N} such that there exists a solution for \emph{D} in
Algorithm \ref{alg:1}. This algorithm gives a unique number for logical
tick delay \emph{d} such that \emph{d} = Min(\emph{$S_2$}) =
Max(\emph{$S_1$}). The compiler, therefore, will choose \emph{d} based
on the newly computed \emph{N} for the examples: Motor and AECS.

@@

The previous results show that HRTCS and Printer were the only examples
that the compiler was able to find \textit{d} without relaxing upper
bound of \texttt{delay}. 
This is because there are two influential factors in
determining the relaxation: 1) execution speed of a target platform and 
%Figure~\ref{fig:graph} shows the accuracy
%of our results by comparing differences between programmer specified
%upper bounds (Table~\ref{fig:benchlist}) and the actual bounds obtained
%using our techniques (Table~\ref{fig:comparison}).
2) the nature of the program that runs on this platform. Clock frequency
of the processor directly impacts the value of WCRT. On the other hand,
programmer can write a program such that large data (or control)
computations in a single logical tick increase WCRT of the program.
Assuming we do not change the architecture of the execution platform
(i.e. JOP), the size of relaxation can only be reduced by modifying the
benchmark programs such that the critical paths are broken up using
\texttt{pause} constructs, thereby reducing the WCRT.
Figure~\ref{fig:improv} shows segments of code from AECS whose WCRT is
reduced by such technique.

\begin{figure}[h!]
	\centering
	\begin{SubFloat}{\label{fig:improv-a}Original program}
    \begin{minipage}[b]{0.3\linewidth}
			\scriptsize
\begin{verbatim}
present(EntryRequest)
  id = #EntryRequest;
else
  id = #ExitRequest;
if(E.isValiedRequest(id)){
  // code ..
}
\end{verbatim}
\end{minipage}
\end{SubFloat}
  \hspace{1cm}%
  \begin{SubFloat}{\label{fig:improv-b}Program with reduced WCRT}
    \centering
    \begin{minipage}[b]{0.35\linewidth}
      \scriptsize
\begin{verbatim}
present(EntryRequest)
  id = #EntryRequest;
else
  id = #ExitRequest;
pause; // Inserting pause
if(E.isValiedRequest(id)){
  // code ..
}
\end{verbatim}
		\end{minipage}
	\end{SubFloat}
	\caption{Improving WCRT by shortening a critical path}
	\label{fig:improv}
\end{figure}

In Figure~\ref{fig:improv-a}, the program simply checks for the id of a
person entering or exiting an intelligent room through the signals
called \texttt{EntryRequest} and \texttt{ExitRequest}, and verifies the
id using data logic written in Java (\texttt{isValidRequest}). We
identified this execution path caused lengthening the WCRT of the
program. In this case, we divide two consequtive statements, i.e.
\texttt{present} and \texttt{if}, by inserting \texttt{pause} such that
each of these statement is executed in two different ticks. The same
technique is applied to Motor example to reduce WCRT of the program.
Note that we can also optimize algorithms of the data computations used
in each Java method to reduce WCRT. However it is out of scope of this
paper, hence not discussed here.

The result of the upper bound relaxation with reduced WCRT is shown in
Figure~\ref{fig:graph}. As one can see from the Figure, the upper bounds
for delay statements in AECS/CD2 has been decreased by 11.81\% which is
higher than all those in Motor which ranges from 7.54 to 8.05\%. It is
because AECS has relatively a large amount of data computation while
Motor is a completely control-dominated program. Therefore, the result
shows that the size of the relaxation depends on how designers write
their program as well as types of the application (i.e. data or control
dominated).

%For AECS/CD2, the upper bound has been reduced
%by 11.81\%, whereas for Motor, the reduced size ranges from 7.54 to
%8.05\% for each delay statement.

\begin{figure}[ht!]
	\centering
%\begin{tikzpicture}[scale=0.9]
%  \begin{axis}[
%      ybar,xtick=data,
%      symbolic x
%      coords={AECS/CD2},
%      height=5cm,
%      width=9.5cm,
%      minor y tick num=1,
%      yminorgrids=true,
%      ymajorgrids=true,
%      xlabel=Benchmark,
%      ylabel=Percentage reduction,
%    ]
%      \addplot coordinates
%      {(AECS/CD2, 11.82)};
%  \end{axis}
%\end{tikzpicture}
\begin{tikzpicture}[scale=0.9]
	\begin{axis}[
			ybar,xtick=data,
			symbolic x coords={Motor,AECS/CD2},
			ytick={0,1,...,12},
			ymin={6},
			minor y tick num=1,
			enlarge x limits=0.5,
			enlarge y limits=0.1,
			yminorgrids=true,
			ymajorgrids=true,
			height=7cm,
			width=9.5cm,
			xlabel=Benchmark,
			xlabel shift={4pt},
			ylabel=Percentage reduction (\%),
			legend style={
				anchor=north,
				at={(0.45,-0.29)},
				legend columns=-1,
			}
		]
			\addplot coordinates {(Motor, 8.05) (AECS/CD2, 11.82)};
			\addplot coordinates {(Motor, 8.00)};
			\addplot coordinates {(Motor, 6.42)};
			\addplot coordinates {(Motor, 7.53)};
			\addplot coordinates {(Motor, 7.89)};
			\legend{Delay1,Delay2,Delay3,Delay4,Delay5}
	\end{axis}
\end{tikzpicture}
\caption{Reduction in upper bound relaxation with improved WCRT}
\label{fig:graph}
\end{figure}

@@

% As one can see in Figure \ref{fig:comparison}, BCRT and WCRT of overall programs
% are smaller when they run on TP-JOP. For example, WCRT and BCRT of HRTCS are
% \(\times\)11.9 and \(\times\)3.4 smaller, respectively, for TP-JOP (0.0028,
% 0.0329 ms) compared to JOP (0.0334, 0.1120 ms). On the other hand, required
% logical delays \emph{d} are generally bigger on TP-JOP e.g. \(\times\)4.5 -
% \(\times\)5.9 and \(\times\)30.9 in Motor and Robot respectively. It is expected
% as their BCRT and WCRT differences are bigger on TP-JOP.
% This also led to greater increase in minimum upper real-time bounds \emph{N} for
% TP-JOP in every example.
% In AECS, there are two clock-domains using delay constructs that each has their
% own BCRT and WCRT. Again, individual BCRT and WCRT is smaller whereas \emph{d}
% is bigger on TP-JOP. One important property to note here, is that BCRT and WCRT
% of any clock-domains are invariant of \emph{d} as explained in Section
% \ref{sec:intr-real-time}. It is our fundamental assumption to find \emph{d} in
% our benchmark programs.
% >>>>>>> 4bffc4b1a43388f5ebf6cc737b9d3b246ee77dc7
